Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-10 WSSSPE1_report/WSSSPE1_summary_report.tex
Fix a compilation error.
Adding MINRES-QLP paper to the relevant sections.
fix author problem

\author{Daniel S. Katz$^{(1)}$, Hilmar Lapp$^{(2)}$, Ketan Maheshwari$^{(3)}$, Frank L\"{o}ffler$^{(4)}$, Matthew Turk$^{(5)}$, Marcus D. Hanwell$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$, James Hetherington$^{(9)}$, James Howison$^{(9)}$, Sou-Cheng T. Choi$^{(10)}$, Shel Swenson$^{(11)}$,  Bruce Berriman$^{(12)}$, Andy R. Terrel$^{(13)}$, Colin Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ xxx}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ xxx}
%
\thanks{{}$^{(8)}$ xxx}
%
\thanks{{}$^{(9)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

Some of the work by Katz was
supported by the National Science Foundation while working at the
Foundation; any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not
necessarily reflect the views of the National Science Foundation. HL
was supported by the National Evolutionary Synthesis Center (NESCent), 
NSF #EF-0905606.

>>>>

\author{Daniel S. Katz$^{(1)}$, Hilmar Lapp$^{(2)}$, Ketan Maheshwari$^{(3)}$, Frank L\"{o}ffler$^{(4)}$, Matthew Turk$^{(5)}$, Marcus D. Hanwell$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$, James Hetherington$^{(8)}$, James Howison$^{(9)}$, Sou-Cheng T. Choi$^{(10)}$, Shel Swenson$^{(11)}$,  Bruce Berriman$^{(12)}$, Andy R. Terrel$^{(13)}$, Colin Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ xxx}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ xxx}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

Some of the work by Katz was
supported by the National Science Foundation while working at the
Foundation; any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not
necessarily reflect the views of the National Science Foundation. HL
was supported by the National Evolutionary Synthesis Center (NESCent), 
NSF \#EF-0905606.
